---
title: "Data processing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Author: Jinxu Xiang

In this file, I did two steps. First,I processed the raw textual data 'lyrics.RData' saved in 'data' file by cleaning data, removing stopwords and creating a tidy version of texts which is saved in 'output' file. 
Then,I combined the processed text with artist information 'artists.csv' and saved the joint data in 'output' file. The 'Origin' column of joint data contains the name of city and country (or state in America). So I extracted the names of each reigon and saved it as 'Precessed_country'.

```{r, message=FALSE, warning=FALSE,echo=FALSE}
packages.used=c("tm", "tidytext","tidyverse","DT","wordcloud","scales","gridExtra","ngram","igraph","ggraph","rsconnect")

# check packages that need to be installed.
packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))
# install additional packages
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}

# load packages
library(tm)
library(tidytext)
library(tidyverse)
library(DT)
library(wordcloud)
library(wordcloud2)
library(scales)
library(gridExtra)
library(ngram)
library(igraph)
library(ggraph)
library(rsconnect)
library(ggplot2)
library(shiny)
library(data.table)
```

```{r read data, warning=FALSE, message=FALSE, echo=FALSE}
# The next few steps are used to initially process the data.
# I saved all processed data in 'output' file.
# If you need to load directly, you can skip to 'r load data' in main rmd.

# load lyrics data
load('../data/lyrics.RData') 
```

```{r text processing in tm, warning=FALSE, message=FALSE, echo=FALSE}
# function for removimg leading and trailing whitespace from character strings 
leadingWhitespace <- content_transformer(function(x) str_trim(x, side = "both"))
# remove stop words
data("stop_words")
word <- c("lot", "today", "months", "month", "wanna", "wouldnt", "wasnt", "ha", "na", "ooh", "da",
        "gonna", "im", "dont", "aint", "wont", "yeah", "la", "oi", "nigga", "fuck",
          "hey", "year", "years", "last", "past", "feel")
stop_words <- c(stop_words$word, word)
# clean the data and make a corpus
corpus <- VCorpus(VectorSource(dt_lyrics$lyrics))%>%
  tm_map(content_transformer(tolower))%>%
  tm_map(removePunctuation)%>%
  tm_map(removeWords, character(0))%>%
  tm_map(removeWords, stop_words)%>%
  tm_map(removeNumbers)%>%
  tm_map(stripWhitespace)%>%
  tm_map(leadingWhitespace)
```

```{r stemming, warning=FALSE, message=FALSE, echo=FALSE}
stemmed <- tm_map(corpus, stemDocument) %>%
  tidy() %>%
  select(text)
```

```{r tidy dictionary, warning=FALSE, message=FALSE, echo=FALSE}
dict <- tidy(corpus) %>%
  select(text) %>%
  unnest_tokens(dictionary, text)
```

```{r tidy stems with dictionary, warning=FALSE, message=FALSE, echo=FALSE}
completed <- stemmed %>%
  mutate(id = row_number()) %>%
  unnest_tokens(stems, text) %>%
  bind_cols(dict) 
```

```{r stem completion, warning=FALSE, message=FALSE, echo=FALSE}
completed <- completed %>%
  group_by(stems) %>%
  count(dictionary) %>%
  mutate(word = dictionary[which.max(n)]) %>%
  ungroup() %>%
  select(stems, word) %>%
  distinct() %>%
  right_join(completed) %>%
  select(-stems)
```

```{r reverse unnest, warning=FALSE, message=FALSE, echo=FALSE}
completed <- completed %>%
  group_by(id) %>%
  summarise(stemmedwords= str_c(word, collapse = " ")) %>%
  ungroup()
```

```{r cleaned hm_data, warning=FALSE, message=FALSE, echo=FALSE}
dt_lyrics <- dt_lyrics %>%
  mutate(id = row_number()) %>%
  inner_join(completed)
```

```{r export data lyrics, warning=FALSE, message=FALSE, echo=FALSE}
save(dt_lyrics, file="../output/processed_lyrics.RData")
```

```{r load data lyrics, warning=FALSE, message=FALSE, echo=FALSE}
# load artist information
dt_artist <- fread('../data/artists.csv') 
# join two data by artist
dt_join = left_join(dt_lyrics, dt_artist, by = c('artist' = 'Artist')) %>%
  mutate(artist = ifelse(is.na(artist), 'Other', artist)) %>% 
  select(-song, -lyrics, -Intro, - Formed, -Members) %>% 
  filter(year > 1900)

# Change all American cities' name in Origin to 'American' and only leave country names.

dt_country = dt_join %>% 
  separate(Origin, into = c('city','country'), sep = ',') %>%
  mutate(country= ifelse(is.na(country), 'Other', country)) %>%
  mutate(country = substr(country, 2, nchar(country))) 

state_to_name = dt_country$country %>% unique()
state_to_name = state_to_name[substr(state_to_name,1,2) %in% state.abb]
state_to_name = tibble(state = state_to_name) %>% 
  mutate(num = map_dbl(state, ~which(substr(.x,1,2) == state.abb))) %>% 
  mutate(name = state.name[num]) %>% 
  select(-num)

dt_country = dt_country %>% left_join(state_to_name, by = c('country' = 'state')) %>% 
  mutate(country = ifelse(is.na(name), country, name)) %>%
  arrange(country) %>% 
  select(-city, -name)
```

```{r export data join, warning=FALSE, message=FALSE, echo=FALSE}
save(dt_join, file="../output/processed_join.RData")
save(dt_country, file="../output/processed_country.RData")
```



